\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-06-08 doc/paper.tex
fixed typos in last edit.

A.V.\ would like to thank Florian Staub for countless explanations of
SARAH's internals, discussions, and exceptionally fast bug fixing.
Finally the authors thank Philip Diessner for testing and identifying
bugs in the MRSSM model file, as well as Ulrik Günther for compilation
tests on Mac OS X\@.

>>>>

A.V.\ would like to thank Florian Staub for countless explanations of
SARAH's internals, discussions, and exceptionally fast bug
fixing. P.A.~would like to thank Roman Nevzorov for useful discussions
about challenges in non-minimal SUSY models. The authors would also
like to thank Lewis Tunstall for helping with early tests against
Next-to-Minimal Softsusy; Sophie Underwood for discovering problems
introducing couplings with a single family index; Philip Diessner for
testing and identifying bugs in the MRSSM model file; Ulrik Günther
for compilation tests on Mac OS X\@ and Dylan Harries for spotting
a bug in the configuration script.
